true

### 2020-04-27 analysis/robinson2020.Rmd
getting travis working

```{r treering-spds}
calibrate_tree_ring_dates <-
  function(x, timeRange = c(50000, 0)) {
    out <- list(
      metadata = tibble::tibble(
        DateID = 1:length(x),
        CRA = x,
        Error = 0,
        Details = NA,
        CalCurve = "intcal13",
        ResOffsets = 0,
        ResErrors = 0,
        StartBP = timeRange[1],
        EndBP = timeRange[2],
        Normalised = TRUE,
        F14C = FALSE,
        CalEPS = 1e-05
      ),
      grids = NA,
      calmatrix =
        tibble::tibble(
          index = 1:length(x),
          year_bp = x,
          value = TRUE
        ) %>%
          tidyr::pivot_wider(
            names_from = index,
            values_from = value
          ) %>%
          dplyr::bind_rows(tibble::tibble(year_bp = timeRange[1]:timeRange[2])) %>%
          dplyr::filter(!duplicated(year_bp)) %>%
          dplyr::arrange(-year_bp) %>%
          dplyr::filter(year_bp >= 0) %>%
          tibble::column_to_rownames("year_bp") %>%
          as.matrix() %>%
          tidyr::replace_na(0) %>%
          magrittr::set_colnames(NULL)
    )

>>>>

```{r treering-spds, results = 'hide'}

gc()
gc()

calibrate_tree_ring_dates <-
  function(x, timeRange = c(50000, 0)) {
    out <- list(
      metadata = tibble::tibble(
        DateID = 1:length(x),
        CRA = x,
        Error = 0,
        Details = NA,
        CalCurve = "intcal13",
        ResOffsets = 0,
        ResErrors = 0,
        StartBP = timeRange[1],
        EndBP = timeRange[2],
        Normalised = TRUE,
        F14C = FALSE,
        CalEPS = 1e-05
      ),
      grids = NA,
      calmatrix =
        tibble::tibble(
          index = 1:length(x),
          year_bp = x,
          value = TRUE
        ) %>%
          tidyr::pivot_wider(
            names_from = index,
            values_from = value
          ) %>%
          dplyr::bind_rows(tibble::tibble(year_bp = timeRange[1]:timeRange[2])) %>%
          dplyr::filter(!duplicated(year_bp)) %>%
          dplyr::arrange(-year_bp) %>%
          dplyr::filter(year_bp >= 0) %>%
          tibble::column_to_rownames("year_bp") %>%
          as.matrix() %>%
          tidyr::replace_na(0) %>%
          magrittr::set_colnames(NULL)
    )
